---
title: "Assignment_03_607"
author: "Mahmud Hasan Al Raji"
date: "`r Sys.Date()`"
output: html_document
---

## Required libraries
```{r}
library(dplyr)
library(htmltab)
library(stringr)
```

## 1:Identification of majors that contain either "DATA" or "STATISTICS" from Majors dataset,data source:[https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/]

```{r}
file<- "https://projects.fivethirtyeight.com/mid-levels/college-majors/"
table1<-htmltab(doc =file, which =1)
str(table1)
majors<-table1$MAJOR
matching <- str_detect(majors, "(?i)statistics|(?i)data")
majors[matching]
```
## 2:Transformation of data to a character vector
**given data:
[1] “bell pepper” “bilberry” “blackberry” “blood orange”
[5] “blueberry” “cantaloupe” “chili pepper” “cloudberry”
[9] “elderberry” “lime” “lychee” “mulberry”
[13] “olive” “salal berry”

**required out put:
c(“bell pepper”, “bilberry”, “blackberry”, “blood orange”, “blueberry”, “cantaloupe”, “chili pepper”, “cloudberry”, “elderberry”, “lime”, “lychee”, “mulberry”, “olive”, “salal berry”)

```{r}
myword <-('[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"')

myword1<-str_extract_all(myword, regex("\\w+..\\w+"))
myword2<-unlist(myword1)
class(myword2)
myword2
```
## 3: Description of expressions

**(.)\1\1: any one character repeated twice

**"(.)(.)\\2\\1": a string whose any two characters repeated once but in reverse way

**(..)\1: a pair of any characters repeated once

**"(.).\\1.\\1": a string whose one character (any type) repeated twice with two consecutive periods where each period consisted of one character(any type) 

"(.)(.)(.).*\\3\\2\\1" : a string whose three characters (any type) followed by 0 or more characters of any type  followed by the first three characters in a reverse way 

## 4:Construction of regular expressions to match words:

**matching-1:Start and end with the same character:"(.).+\1$"

```{r }
matching1<- c("apa", "lol", "nope", "mango", "eighteen")
str_view(matching1, "(.).+\\1$", match=TRUE)
```

**matching-2:Contain a repeated pair of letters:"(..).+\1"

```{r }
matching1<- c("church", "ppeppero", "nope", "mango", "eighteen")
str_view(matching1, "(..).+\\1", match=TRUE)
```

**matching-3: Contain one letter repeated in at least three places:"([a-zA-Z])....\1+\1.+"

```{r }
matching3<- c("okra", "papaya", "banana", "mango", "eighteen")
str_view(matching3, "([a-zA-Z])....\\1+\\1.+", match=TRUE)
```

